A Two-Infall Star Formation History with Outflows and Radial Migration

### 2025-02-05 src/tex/ms.tex
Updates from Overleaf

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Yields
        y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
        f_{\rm Ia}(t)   & Plateau   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
        % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
        % Star formation histories
        % Outflows
        \eta_\odot      & 0.4       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
        R_\eta          & 5.4 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
        % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
        \tau_1          & 1 Gyr     & \ref{sec:sfh}     & Timescale of the first infall epoch \\
        \tau_2          & 15 Gyr    & \ref{sec:sfh}     & Timescale of the second infall epoch \\
        t_{\rm max}      & 4.2      & \ref{sec:sfh}     & Time of maximum gas infall (onset of second infall) \\
        f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
        {\rm [X/H]}_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
    \enddata
\end{deluxetable*}
\vspace{-24pt}

@@

We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\odot=8$ kpc. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
\begin{equation}
    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
\end{equation}
We adopt $R_\eta=5.4$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.08$ dex kpc$^{-1}$.
\todo{Motivate exponential scale radius.}

>>>>

\begin{deluxetable*}{Cccl}
    \tablecaption{A summary of variables and their fiducial values for our chemical evolution models (see discussion in Section \ref{sec:methods}).\label{tab:multizone-parameters}}
    \tablehead{
        \colhead{Quantity} & \colhead{Fiducial Value(s)} & \colhead{Section} & \colhead{Description}
    }
    \startdata
        % Yields
        y/Z_\odot       & 1         & \ref{sec:yields}  & Nucleosynthetic yield scaling (see Table \ref{tab:yields}) \\
        N_{\rm Ia}/M_\star  & $1.55\times10^{-3}$       & \ref{sec:yields}  & Integrated Type Ia supernova rate (see Table \ref{tab:yields}) \\
        f_{\rm Ia}(t)   & Plateau   & \ref{sec:yields}  & Delay-time distribution of Type Ia supernovae \\
        % t_D             & 40 Myr    & \ref{sec:yields}  & Minimum SN Ia delay time \\
        % Star formation histories
        % Outflows
        \eta_\odot      & 0.4       & \ref{sec:outflows}    & Outflow mass-loading factor in the Solar annulus ($\eta\equiv \dot\Sigma_{\rm out}/\dot\Sigma_\star$) \\
        R_\eta          & 7.2 kpc   & \ref{sec:outflows}    & Exponential outflow scale radius \\
        % f_{\rm in}(t|R_{\rm gal})   & Equation \ref{eq:infall-rate}   & \ref{sec:sfh} & Time-dependence of the gas infall rate \\
        \tau_1          & 1 Gyr     & \ref{sec:sfh}     & Timescale of the first infall epoch \\
        \tau_2          & 15 Gyr    & \ref{sec:sfh}     & Timescale of the second infall epoch \\
        t_{\rm max}      & 4.2      & \ref{sec:sfh}     & Time of maximum gas infall (onset of second infall) \\
        f_{\Sigma,0}    & 0.27      & \ref{sec:sfh}     & Central thick/thin disk surface density ratio \\
        {\rm [X/H]}_{\rm CGM}   & Pristine  & \ref{sec:sfh}     & Metallicity of infalling gas \\
        \sigma_{\rm RM8}    & 2.68 kpc  & \ref{sec:migration}   & Radial migration strength
    \enddata
\end{deluxetable*}
\vspace{-24pt}

@@

We adopt a fiducial prescription for the outflow mass-loading factor which increases exponentially with radius:
\begin{equation}
    \eta(R_{\rm gal}) = \eta_\odot \exp\Big(\frac{R_{\rm gal}-R_\odot}{R_\eta}\Big)
\end{equation}
where $R_\odot=8$ kpc. As discussed by \citet{johnson_milky_2024}, the exponential outflow scale radius $R_\eta$ sets the equilibrium abundance gradient $\nabla{\rm [O/H]}_{\rm eq}$:
\begin{equation}
    R_\eta = -\frac{1}{\nabla{\rm [O/H]}_{\rm eq} \times\ln(10)}.
\end{equation}
We adopt $R_\eta=7.2$ kpc as our fiducial value, which corresponds to $\nabla{\rm [O/H]}_{\rm eq}=-0.06$ dex kpc$^{-1}$.
\todo{Motivate exponential scale radius.}
